---
title: "languages_unesco"
author: "luciana"
date: "10/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}

# Load Tidyverse, janitor and arcos, tidycensus, mapview, ggthemes, scales


library(tidyverse)
library(janitor)
library(arcos)
library(tidycensus)
library(mapview)
library(ggthemes)
library(scales)
library(ggrepel)


```



UNESCO allows you to download a file containing limited information on all the languages listed in the Interactive Atlas.
The limited data include the following types of data for all the languages listed in the Atlas:
  
Language name in English
Language name in French
Language name in Spanish
Country(ies) or area(s) where the language is spoken
Country code(s)
Language codes ISO 639-3



Degree of vitality - 

The present edition designates the degrees of endangerment a little differently than the previous editions. The new terminology is based on UNESCO’s Language Vitality and Endangerment framework that establishes six degrees of vitality/endangerment based on nine factors. Of these factors, the most salient is that of intergenerational transmission.


Degree of endangerment	Intergenerational Language Transmission
1. Safe- language is spoken by all generations; intergenerational transmission is uninterrupted. Not included in the Atlas
2. Vulnerable	- vulnerable	most children speak the language, but it may be restricted to certain domains (e.g., home)
3. Definitely endangered	- definitely endangered	children no longer learn the language as mother tongue in the home
4. Severely endangered	- severely endangered	language is spoken by grandparents and older generations; while the parent generation may understand it, they do not speak it to children or among themselves
5. Critically endangered	- critically endangered	the youngest speakers are grandparents and older, and they speak the language partially and infrequently
6. Extinct - 	extinct	there are no speakers left -  included in the Atlas if presumably extinct since the 1950s
  

```{r}

unesco_atlas_languages_limited_dataset <- unesco_atlas_languages_limited_dataset %>% clean_names()


``` 



```{r}
 unesco_atlas_languages_limited_edited <-unesco_atlas_languages_limited_dataset %>% select(name_in_english,countries,country_codes_alpha_3,degree_of_endangerment)

```


```{r}
#FILTER FOR ONLY USA 
usa_langauges <- unesco_atlas_languages_limited_edited %>% 
  filter(country_codes_alpha_3 == 'USA')%>% 
  select(name_in_english,degree_of_endangerment)
```


```{r}
#Bar graphs of it

 options(scipen=999)
 

  ggplot(usa_langauges) +
  geom_bar(stat="identity", aes(degree_of_endangerment,name_in_english), fill="royal blue") +
  labs(x="degree of vitality", y="total languages", title="vitality", subtitle = "Total pills shipped to Baltimore City by year", caption = "Source: DEA ARCOS database, via Washington Post")
  
  # Also saves a web version
  ggsave("usa_langauges", plot=last_plot())

```


